Proper radial distance as a coordinate in the Schwarzschild metric

### 2022-06-19 arxiv/template.tex
slight rewording

\begin{abstract}
The Schwarzschild solution to the spherically symmetric vacuum
Einstein field equations is usually presented in terms of
Schwarzschild coordinates $(t,r,\phi,\theta)$.  However, we are free
to consider reparametrizations in terms of functions of the
Schwarzschild coordinates.  Here I consider the Schwarzschild solution
in terms of $(t,u_1\phi,\theta)$, where $u_1=u_1(r)$ is the
straight-line proper length from a point to the event horizon.  This
coordinate system has some interesting properties and affords new
physical insight to black holes.  I also consider related
parameterizations $u_2$ and $u_3$ which preserve proper area or volume
instead of proper length.
\end{abstract}

% keywords can be removed
\keywords{First keyword \and Second keyword \and More}

\section{Introduction}
The Schwarzschild metric is usually written

>>>>

\begin{abstract}
The Schwarzschild solution to the spherically symmetric vacuum
Einstein field equations is usually presented in terms of
Schwarzschild coordinates $(t,r,\phi,\theta)$, where $r$ is the
circumferential radius.  However, we are free to consider
reparametrizations in terms of functions of the Schwarzschild
coordinates.  Here I consider the Schwarzschild solution in terms of
$(t,u_1,\phi,\theta)$, where $u_1=u_1(r)$ is the straight-line proper
length from a point to the event horizon.  This coordinate system has
some interesting properties and affords new physical insight to black
holes.  I present some diagrams using proper length radial coordinate
instead of circumferential radius $r$.  I also consider related
parameterizations $u_2$ and $u_3$ which preserve proper area or volume
instead of proper length.
\end{abstract}

% keywords can be removed
\keywords{Black hole\and Proper distance \and Proper radial coordinate\and Schwarzschild metric}

\section{Introduction}
The Schwarzschild metric \citep{schwarzschild1916} is usually written
